---
title: "Student presentations"
subtitle: ""
author: "FISH 521 - Proposal Writing and Professional Development"
date: "6 March 2023"
output:
  html_document:
    theme: darkly
    highlight: textmate
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>

## Background

Your assignment this week is to give a live presentation of your proposal idea **in class** on Mqrch 6. Your presentation should cover the following elements:

* Background and rationale for your proposed research

* Questions of interest (or hypotheses to test)

* Methods/approach

* Anticipated results

* Implications (intellectual merit)


## Evaluation rubric

We will evaluate the quality of your presentation based on the following criteria:

* Title slide with name, affiliation, and contact info

* Acknowledgment of collaborators and funders

* Layout/design of the slides (eg, good color contrast, appropriate font size)

* Speaking clearly and addressing the audience rather than the computer or slides

* Presenting the background and clear rationale for the study

* Brief explanation of the methods or approach

* Highlighting expected results and any potential difficulties

* Brief comment(s) on the implications of the research

* Appropriate ending


## Evaluation Form

(see also email)

https://forms.gle/wuPo9afsGU5WK3ay6


## Presentation upload

Please note that due to our tight time frame in class, **you are required to push your presentation to your GitHub repo no later than 12:30 PM Pacific Standard Time on March 6** 


## Schedule

Here is the schedule for the day. **Note that everyone has a total of 7 minutes for their presentation**. This includes introduction of you and any Q&A.

```{r schedule, echo = FALSE}
library(magrittr)
library(kableExtra)
set.seed(521)

## set class roster
roster <- c(
  "Boggs",
  "Gammelin",
  "Hallock",
  "Henry",
  "Jacuzzi",
  "Kattil-Debrum",
  "Kinneen",
  "Lasdin",
  "Leigh",
  "Mcgreal",
  "Neal",
  "Redon",
  "Skalley",
  "Teman",
  "Vaage",
  "Valdivia",
  "Yerrace",
  "Zhang"
  )

## order of presentations
p_order <- c(sample(roster, length(roster)))

## people & breaks
items <- c("**[ Introduction ]**", p_order[1:7], "**[ Break ]**",
           p_order[8:14], "**[ Break ]**", p_order[15:20], "**[ Wrap-up ]**")

## date of presentations
start_date <- as.POSIXct("2022-02-28 13:30")
## dates in seconds past `start_date`
dates_sec <- c(0, 48, 96, 97, 98) * 3600
## presentation & break times in seconds past the hour
p_times_1 <- seq(5, by = 7, length.out = 7)
break_1 <- 54
p_times_2 <- seq(65, by = 7, length.out = 7)
break_2 <- 113
p_times_3 <- seq(125, by = 7, length.out = 7)
times <- c(0, p_times_1, break_1, p_times_2, break_2, p_times_3) * 60
## formal times
date_times <- start_date + times

## nicer formatting
date_times <- as.POSIXct(date_times, origin = "1970-01-01")
date_times <- format(date_times, "%I:%M")
## drop leading 0
date_times <- sub("0(\\d)", "\\1", date_times)

## full schedule
schedule <- data.frame(Time = date_times,
                       Speaker = items)

## create & print table
kableExtra::kable(schedule, format = "html", caption = " ",
                  align = "cc", escape = FALSE) %>%
  kable_styling(bootstrap_options = "striped",
                full_width = FALSE,
                position = "left") %>%
  column_spec(1, width = "6em") %>%
  column_spec(2, width = "15em")
```




